Modeling and Simulation of Online Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor

### 2018-05-10 highlights/highlights.tex
adds highlights and graphical abstract

\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
\newcommand{\Cycamore}{\textsc{Cycamore}\xspace}%
\graphicspath{ {images/} }

@@

\begin{document}
\begin{frontmatter}
\title{Graphical Abstract\\
Modeling and Simulation of Online Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor}
\date{}                     %% if you don't need date to appear

\end{frontmatter}

\begin{figure}[htbp!]
    \begin{center}
        \includegraphics[width=\textwidth]{./highlight.png}
    \end{center}
    \caption{A very fancy image important to the paper.}
    \label{fig:graph-abs}
\end{figure}

\end{document}

>>>>

\graphicspath{ {figures/} }

@@

\begin{document}
\begin{frontmatter}
\title{Modeling and Simulation of Online Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
       \item Highlight 1
       \item Highlight 2
       \item Highlight 3
\end{itemize}
\end{document}
